---
title: "LaTeX image table template"
author: "Chris Tufts @devlintufts"
date: "November 6, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r pressure, echo=FALSE}
# create file lists
plot_file_0 <- list.files('figures/0/', full.names = T, recursive = F)[1:5]
plot_file_1 <- list.files('figures/1/', full.names = T, recursive = F)[1:5]


```
\begin{tabular}{|c|c|c|c|c|c|}
      \hline
      Plots from directory 2 &
      \includegraphics[width=20mm]{`r plot_file_0[1]`} &
      \includegraphics[width=20mm]{`r plot_file_0[2]`} &
      \includegraphics[width=20mm]{`r plot_file_0[3]`} &
      \includegraphics[width=20mm]{`r plot_file_0[4]`} &
      \includegraphics[width=20mm]{`r plot_file_0[5]`} \\
      \hline
      Plots from directory 1 &
      \includegraphics[width=20mm]{`r plot_file_1[1]`} &
      \includegraphics[width=20mm]{`r plot_file_1[2]`} &
      \includegraphics[width=20mm]{`r plot_file_1[3]`} &
      \includegraphics[width=20mm]{`r plot_file_1[4]`} &
      \includegraphics[width=20mm]{`r plot_file_1[5]`} \\
      \hline
\end{tabular}

